Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-10 man/figures/plot_spei12.Rmd
change color

```{r, fig.height=5}
p <- spei %>% 
  ggplot(aes(x=date, y=spei, fill=sign)) +  
  geom_bar(stat = "identity") + 
  scale_fill_manual(values = c("pos" = "#696969", "neg" = "red")) +
  theme_bw() + 
  geom_hline(yintercept = 0, colour = 'gray') +
  labs(x = '', y ='SPEI (12-month scale)') +
  scale_x_date(date_breaks = "5 year", date_labels = "%Y", 
               limits=as.Date(c("1949-01-01", "2015-12-01"))) +
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "none", 
        panel.grid = element_blank(), 
        axis.text.y = element_text(size=10),
        axis.text.x = element_text(size=9),
        axis.title.y = element_text(size = 12)) 
```

>>>>

```{r, fig.height=5}
p <- spei %>% 
  ggplot(aes(x=date, y=spei, fill=sign)) +  
  geom_bar(stat = "identity") + 
  scale_fill_manual(values = c("pos" = "#696969", "neg" = "brown4")) +
  theme_bw() + 
  geom_hline(yintercept = 0, colour = 'gray') +
  labs(x = '', y ='SPEI (12-month scale)') +
  scale_x_date(date_breaks = "5 year", date_labels = "%Y", 
               limits=as.Date(c("1949-01-01", "2015-12-01"))) +
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "none", 
        panel.grid = element_blank(), 
        axis.text.y = element_text(size=10),
        axis.text.x = element_text(size=9),
        axis.title.y = element_text(size = 12))

p
```
